\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}

\title{SI 710 Assignment 4: Experiment Design}
\author{Linfeng, Merve, Rosina, Tangren}
\date{}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[colorlinks,linkcolor=blue,bookmarksdepth=paragraph]{hyperref}

\begin{document}
\maketitle
\tableofcontents
% Old notes
%\input{notes_pre_Feb13}

\section{Experiment Design}
\subsection{Motivation}
The purpose of this study is to see how the presence of social networks affects
trading patterns and, by extension, the efficiency of decentralized markets.


\subsubsection{Social Network Implementation}
Real world, existing friendships.

\subsection{Experiment Procedure}
\begin{enumerate}
    \item Randomly assign subjects into two groups, treatment and control.
        (Please refer to section ``Subjects, Control and Treatment'')
    \item Elicit network of treatment group (Please refer to section ``Network
        Elicitation Method'')
    \item Computer based trading: treatment with real ID; control with changing
        fake ID. Subject can post unbinding offers publicly but they can
        negotiate (private chatting) as well. (Please refer to section ``Market
        mechanism'')
    \item At the end of each round, subject will observe the average price or
        distribution(we can discuss which one is better) (just like
        ``truecar.com'')
    \item Subject will be reward the surplus they earned in the experiment.
\end{enumerate}

\subsubsection{Subjects, Control and Treatment}
The experiment will be run in a computer-based trading setting among a class of
undergraduate students, such as ECON 102. The main advantage of the selected
group of subjects is the easy access and the fact that we would not need
parental consent. This course is chosen since it is still a mass course and
provides students with enough time to establish a network in college. Hence, the
measured social network will be the existing friendship network among students.

In order to measure the importance of social networks on decentralized
competitive markets and the choice of trading partners, subjects are randomly
selected from the course and assigned into two groups of 25 individuals. The
size of each group is selected to make the elicitation mechanism possible. (if
not it is too long)

In the treatment group, students are identified with their real names which
implies that the subjects are able to recognized trading partners with whom they
have a closer social relationship. After the trading experiment is run, the
social network of the treatment group is going to be elicited. In the control
group, subjects are not identified and are randomly assign with a fake ID. Note
that in both groups, the market design is identical except from the fact that in
one group subjects are identifiable whereas in the other they are not.

The choice of this methodology allows us to identify how the social network
influences the trading patterns among subjects. We expect that subjects are more
likely to trade with individuals who belong to their social network.

\subsection{Market Mechanism}
We are focusing on a computer based double auction environment. The ask and bid
offers are going to be posted in a publicly available fashion. In contrast to
the transparency of the prices, agents will be able to privately chat and
negotiate. The transactions will be realized once both parties agree on it. We
will let sellers to have multiple units, whereas buyers are looking for one unit
of good to purchase. The parties will be charged a small amount that will be
determined with respect to the round of negotiations they make through private
chatting.

\subsection{Network Elicitation Method}
\input{NetworkElicitation}


\subsection{Hypothesis and Testing}
\subsubsection{Hypotheses}
\begin{enumerate}[{Hypothesis} 1]
    \item Subjects will be more likely to trade with individuals who are in
        their social network.
    \item Bargaining costs will be lower when access to social networks is
        available.
    \item Efficiency will be higher in homogeneous good markets when networks
        are available. This is expected to be due to lower trading costs.
    \item Price dispersion will be greater in markets where social networks are
        available. In other words, the Law of One Price is less likely to hold.
    \item Surplus will be split more equally in markets with social networks.
    \item Friends with stronger ``ties'' will trade more items than friends with
        weak ``ties'', if anything at all.
\end{enumerate}

\subsubsection{Testing Hypothesis}
\begin{enumerate}[{Hypothesis} 1]
    \item  Utilizing the elicited network, compute the frequency to within network
        transaction of treatment group, compare it with no network effect
        probability.
    \item  Compute means and standard deviations of bargaining time of control
        group, treatment group ( a.total transactions; b.transactions within
        network; c. transactions outside of network), then calculate $p$-value to check
        statistic significance.
    \item  Compute total surplus achieved in each round in both control and
        treatment, then calculate the statistic difference of these two.
    \item Compute means and standard deviations of price dispersion in each round of
        control group, treatment group ( a.total transactions; b.transactions within
        network; c. transactions outside of network), then calculate $p$-value to check
        statistic significance.
    \item Compute means and standard deviations of surplus splitting ratio (sell
            surplus/buyer surplus) in each round of control group, treatment group (
            a.total transactions; b.transactions within network; c. transactions outside of
        network), then calculate $p$-value to check statistic significance.
\end{enumerate}



\section{Notes from Lecture 7 on Feb 15, feedbacks + thoughts }

\subsection{Feedback on the experiment design proposed as draft}
Written in a tone of a group project, with a group meeting on Feb 21, 2016 in
head.

\subsubsection{Problems}

\begin{enumerate}
    \item How to let the subjects in the treatment group recognize their
        friends?
        \begin{itemize}
            \item If through photos, then other traits shall penetrate: say,
                girls would like to trade with girls, and boys may offer
                discount for beautiful ladies \& \textit{vise versa}.
            \item $\implies$ maybe, we may use the real names to
                for agents to recognize each other?

                May consider introduce the confounding ``human-recognition''
                step-by-step:
                \begin{enumerate}
                    \item For Treatment Group I: use only the name;
                    \item For Treatment Group II: use name + photos (or photos
                        only)
                \end{enumerate}
                To further elicit the effect of photos, may:
                \begin{itemize}
                    \item[(c)] Introduce another control group, where agents with
                        random IDs are identified through (randomly assigned?)
                        photos.
                \end{itemize}
        \end{itemize}
    \item What would the chatting channel brings:
        \begin{itemize}
            \item Chatting feature may introduce various confounds\footnote{\textcolor{green}{Chatting is already costly via:\\
            \begin{enumerate}
                \item they might miss a good price in the market while chatting
                \item they might be embarrassed to ask for a lower/higher price
            \end{enumerate}} }. Two ways out:
                \begin{enumerate}
                    \item Implement the chat feature in full, and adopt NLP
                        (natural language processing)?
                    \item Remove the chat feature, and let agents only interact
                        through numeric bids \textcolor{green}{Maybe we can have a hypothesis about chatting}.
                \end{enumerate}
        \end{itemize}
    \item Alan's list of questions: missing
        \begin{itemize}
            \item Emails sent to Alan echoed no reply. We may need to prolong
                the network-eliciting survey together.
        \end{itemize}
    \item Could other measure of the elicited network matter for trading
        patterns?
        \begin{itemize}
            \item Had the agents been able to trade more than one good, will the
                distribution of deals be more evenly spread when the set of
                agents involved in the trade belong to a more \textbf{dense}
                network?
            \item Given this, does the clustering, and diameter of network
                matter, when we are observing a vivid market with multiple
                friends trading?
        \end{itemize}
        \item \textcolor{green}{How to make 24 participants appear?
        \begin{itemize}
            \item The amount that will be paid to the participants for an hour, should in expectation be equal to the hourly wage of tutoring (depends on the participant pool, what the alternative occupation wage would be?)
            \item Also, people usually put more effort into the experiment when they are negotiating over larger amount of money, so maybe let's have high numbers/valuations/prices and let's do the payments in laboratory units.
        \end{itemize}}
        \item \textcolor{green}{Maybe put a restriction of, say 10 rounds of negotiating through chatting, instead of the cost that is imposed for the private chatting rounds.}
       \item \textcolor{green}{We expect a convergence-how many rounds should we have in each session?}

\end{enumerate}




%
%\bibliographystyle{plain}
%\bibliography{references}
\end{document}
